A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-08-01 papers/paper1/ms.tex
Added equation from Rackham
Writing prose-- some introduction, some methods, some equation placeholders.

@@

\begin{deluxetable*}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{2015MNRAS.450.3211A} & - & Using Kepler to study stellar rotation \\
  \citet{2022ApJ...924...31B} & - & Estimating the lifetime of starspots based on rotational periods \\
  \citet{2010ApJ...713L.109B} & - & Why Kepler picked particular stars for observation \\
  \citet{2010Sci...327..977B} & - & Using the Kepler mission to discover exoplanets \\
  \citet{2021sf2a.conf..363B} & - & Stellar rotation using ROOSTER \\
  \citet{2022ApJ...927..219C} & - & Deep learning to recover TESS light curves \\
  \citet{2022ApJ...925..185D} & - & Lightcurves for oblate, rapid rotators \\
  \citet{2017ARep...61..122D} & - & Using Kepler to observe starspots on M dwarf stars \\
  \citet{2020RAA....20..167F} & - & Overview of Kepler mission \\
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition \\
  \citet{Kochukhov21} & - & Magnetic fields of M dwarfs \\
  \citet{2021AJ....162..123L} & - & Test Lightcurve and study stellar surfaces \\
  \citet{2022ApJ...933..195M} & - & Comparing rotational periods of sun-like stars versus photometric amplitude \\
  \citet{2020MNRAS.491.2706N} & - & Calculating stellar age based on starspot covering fraction \\
  \citet{2018ApJ...853..122R} & - & TLSE \\
  \citet{Reinhold2013} & - & Measure rotation of active Kepler Stars \\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  \citet{2022MNRAS.511.2285W} & - & Starspots on detached eclipsing binaries (DEBs) \\
  \enddata
\end{deluxetable*}

>>>>

\authorcomment1{General background information and motivation for starspots...}

The simplest observational predictors of starspot physical properties appear to be effective temperature (\emph{i.e} spectral type, mass, and/or evolutionary state) and rotation rate (\emph{i.e.} Rossby number).  Theese terms apparently control the conditions that give rise to spots \censorbox{Cite Mayukh Panja papers}.

Disentangling starspot contrast and area is challenging, since many observables produce degeneracies among these two distinct physical properties.  For example, a given flux loss in a monochromatic time series lightcurve can indicate a large warm starspot or or a small cool starspot.

@@

\begin{deluxetable*}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{2015MNRAS.450.3211A} & - & Using Kepler to study stellar rotation \\
  \citet{2022ApJ...924...31B} & - & Estimating the lifetime of starspots based on rotational periods \\
  \citet{2010ApJ...713L.109B} & - & Why Kepler picked particular stars for observation \\
  \citet{2010Sci...327..977B} & - & Using the Kepler mission to discover exoplanets \\
  \citet{2021sf2a.conf..363B} & - & Stellar rotation using ROOSTER \\
  \citet{2022ApJ...927..219C} & - & Deep learning to recover TESS light curves \\
  \citet{2022ApJ...925..185D} & - & Lightcurves for oblate, rapid rotators \\
  \citet{2017ARep...61..122D} & - & Using Kepler to observe starspots on M dwarf stars \\
  \citet{2020RAA....20..167F} & - & Overview of Kepler mission \\
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition \\
  \citet{Kochukhov21} & - & Magnetic fields of M dwarfs \\
  \citet{2021AJ....162..123L} & - & Test Lightcurve and study stellar surfaces \\
  \citet{2022ApJ...933..195M} & - & Comparing rotational periods of sun-like stars versus photometric amplitude \\
  \citet{2020MNRAS.491.2706N} & - & Calculating stellar age based on starspot covering fraction \\
  \citet{2018ApJ...853..122R} & - & TLSE \\
  \citet{Reinhold2013} & - & Measure rotation of active Kepler Stars \\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  \citet{2022MNRAS.511.2285W} & - & Starspots on detached eclipsing binaries (DEBs) \\
  Mayukh Panja & What do starspots look like \\
  \enddata
\end{deluxetable*}

\section{Methodology}

\subsection{Starspot contrast and temperature}
There does not appear to be a first-principles theoretical prediction for the spectrum of a starspot, as a function of the physical state of the star.  Instead, practitioners have come up with phenomenological models based on observed trends in spot contrast coupled with ostensibly commonsense heuristics.  Most practitioners assume that starspot temperature depends principally on the photospheric temperature.  Two sources provide similar but slightly different trends for this relationship.  \citet{2019AJ....157...96R} distilled the compilation of spot temperatures from \citet{2005LRSP....2....8B} into a simple first order linear relationship:
\begin{equation}
  T_{\mathrm{spot}} = 0.418 \times T_{\mathrm{phot}} + 1620~\mathrm{K}
  \label{eq:Tspot}
\end{equation}

\citet{2016MNRAS.463.2494F} report an ostensibly quadratic dependence on the ambient photosphere, with hot stars asympoting to a typical starspot temperature of $\sim3500~\mathrm{K}$.  This departure from the linear trend could encode an observational bias since the LAMOST TiO-based technique may lack sensitivity to hypotetical hotter spots.  Nevertheless the trend serves as a useful guide in the absence of more, and higher quality, data.  Here we fit a quadratic relationship to the \citet{2016MNRAS.463.2494F} LAMOST-derived temperature points to obtain the relationship:
\authorcomment1{Ryan H. to determine A, B, and C}.

\begin{equation}
  T_{\mathrm{spot}} = a \times T_{\mathrm{phot}}^2 + b \times T_{\mathrm{phot}} + c ~\mathrm{K}
  \label{eq:TspotFang}
\end{equation}

\authorcomment1{Todo: Cite Lyra Cao et al. in prep-- estimated August 2022}.

We plot both trends in Figure \censorbox{X}.  The range of validity and accuracy of these relationships remain unclear. Interrogating these trends forms the main thrust of this work.

\subsection{Starspot contrast from Kepler and TESS}
A typical starspot
